Dynamical Properties of Molecular Gas Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-08-20 WRITEUP/ms.tex
fixed some redudancy after last commit merge

@@

\begin{abstract}
We present results from the first study investigating the dynamical properties of molecular clouds 
and their evolution in galaxies at Epoch of Reionization using state-of-the-art cosmological 
zoom-in simulation, which includes a chemical network to determine the formation of molecular 
hydrogen, heating and cooling of the ISM by metals, and stellar feedback via 
kinetic and thermal energies. We..
\end{abstract}
%\keywords{infrared: galaxies --
%          galaxies: high-redshift --
%          galaxies: ISM --
%          galaxies: evolution --
%          galaxies: starburst --
%          radio lines: ISM}

@@

The growth of galaxies and their subsequent evolution are governed by the baryonic/baryon cycle ---
galaxies accrete gas from the intergalactic medium to fuel \SF (and feed their supermassive blackholes)
and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
The general consensus is that the growth of \highz galaxies are triggered/supported by massive
gas inflows from mergers and/or the cosmic web at early cosmic time, when the intergalactic 
medium and galaxies themselves are more gas-rich in their star-forming molecular 
gas contents compared to present-day galaxies.
 % while at a given snapshot, the gas mass fraction maybe low (esp. at high-z when 
% the gravitational potential is still increasing), but their gas reservoirs 
% are continuously being replenished. 
These massive gas inflows in turn trigger gravitational instability, and thus, lead
to the formation of clouds/structures that are typically more massive and denser than those 
observed in nearby galaxies, with cloud masses of $M_{\rm cloud}$\eq10$^9$\,\Msun 
and sizes on sub-kpc scales (e.g. \citealt{Gabor13a, Hopkins14a, Inoue16a}).
%In cosmological context, minor mergers and external gas accretion can
%significantly impact on disc dynamics and clump formation
%(e.g. Bird et al. 2012, MNRAS, 420, 913; Kyziropoulos et al. 2016, MNRAS, 463, 2210).
Some theoretical works postulate that it is in fact the
migration of such giant massive clumps that are responsible for contributing to the 
buildup of the bulges of massive galaxies at \z$\sim$0 \citep[e.g.,][]{Ceverino10a}.

At high redshifts, galaxies are expected to have lower metallicity, 
% stronger and harder radiation fields),
more \ion{H}{2} regions and ionized gas 
(given their much higher star formation rates; SFR), and 
more intense radiation stellar feedbacks.
Such differences in turn affect the thermal and chemical structures of their ISM (e.g., shielding of UV photons, heating and cooling mechanisms, and elemental abundances),
and thus, their multi-phase ISM differ from nearby galaxies.
Since \highz galaxies are the early stages of evolution of present-day galaxies, 
studying their ISM properties is essential for understanding how \SF proceed under these more extreme
conditions, thereby driving the evolution and assembly history 
of galaxies since the cosmic dark ages.
% since they set the pace for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).

The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO/[\ci]~lines are the key diagnostics for 
constraining the ISM conditions of galaxies and
provide highly complementary information tracing the different phases of the ISM (ionized, 
atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
Global measurements of these diagnostics in \highz galaxies 
have informed us on their galaxy-wide properties (e.g., 
gas masses, gas temperature, and radiation field intensity).
However, spatially resolving their ISM is needed in order to understand their role in galaxy evolution and 
the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
To date, the ISM properties of \highz galaxies 
have only been studied observationally in a handful of (strongly-lensed) 
galaxies, using spatially resolved tracers such as 
dust continuum, and CO and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
Leung et al. 2018, submitted).
These studies find that the ISM of $z$\ssim2 galaxies are more 
molecular gas-rich, turbulent, and clumpy than nearby galaxies.
However, it is still unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6 
that dominates  \SF at the epoch of reionization which is responsible for producing the 
ionizing photons that reionized the universe.

@@

This paper is structured as follows.
In \Sec{sim}, we describe the setup of our simulation and the properties of our galaxy (\flower),
and describe the method used to identify its molecular gas complexes (MC). 
In \Sec{results}, we present scaling relations based on 
the MC identified and compare them with observations of molecular 
(sub-)structures seen in nearby and \z$>$\,0 galaxies.
We present Toomre stability analysis in \Sec{Q} and 
the cumulative mass distribution of the MCs in \flower in \Sec{cmf}.
In \Sec{diss}, we discuss the results and implications of our findings,
and present our conclusions in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities 
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, 
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, 
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

@@

\ncode{Serra} is a cosmological zoom-in simulation performed using Eulerian hydrodynamics and 
adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high baryonic density).
In particular, it uses a modified version of \ncode{ramses} as the AMR backend.
\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and 
photoevaporation feedback in the neutral diffuse and molecular gas. 
Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving 
down to a physical scale of 30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the 
finest level.
Such a physical scale is close to the size scale of molecular cloud complexes and
giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
% (Giant molecular clouds: L>22pc, m>10^5 Msun) in MW.
We include chemical network in the simulation to trace 
$\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
Of particular importance to our study here is that 
our simulation includes non-equilibrium formation of molecular 
hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of 
chemistry affected by non-equilibrium versus equilibrium H$_2$ formation). 
Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}.
We adopt stellar tracks from \ncode{starburst99} and 
include stellar feedback from supernova, OB/AGB stars to account for energy dissipations.
The energy dissipated is then injected into the ISM in the form of kinetic and thermal energy.
Radiation pressure (on the dust and gas) is also included.  % radiative feedback --> NT pressure
To couple the feedback to the gas, we 
employ sub-grid modeling for blastwaves to account for the potential lost of energy inside the cell when
supernovae are exploded.

Details of how \flower, the main galaxy in our simulation,
was identified is discussed in detail by \citet{Pallottini17a}.
Briefly, by \z$\sim$6, \flower is a LBG hosted in 
a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and 
accretes mass from the intergalactic medium mainly via three filaments of length $\simeq$\,100\,kpc.
At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun,
metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$,
a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun,
and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne\footnote{This includes contributions from its nearby massive satellite galaxies.}.
It is therefore a prototypical galaxy at \z$\sim$6.

\subsection{``Clump''-finding} \label{sec:method}

To identify the molecular complexes, we use a customized version of the clump finder algorithm 
available in the \ncode{python} package \ncode{yt}, which was initially described in \citet{Smith09a}
but this function has been modified since then.
The latest version of the default \ncode{yt} clump finder decomposes the cells in the simulation
into non-overlapping tiles, which are stored in a k-dimentional tree (aka k-d tree).
It then identifies the contours of a variable field (e.g., density field) within a tile and connects them across 
the tiles. In the customized version used for this study, we modified \ncode{yt} in order for it to actually work.

In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
We note that this process is in essence similar to 
identifying molecular structures based on the noise levels of surface density maps 
observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
as commonly adopted in observational studies (e.g., identifying 
``clumps'' based on/after applying $\sigma$-clipping, 
using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, 
and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a}).

\begin{figure}[Htbp]
\centering
\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}  
\caption{
Volumetric H$_2$ density distribution of \flower taken from a single snapshot.
\label{fig:h2density}}
\end{figure}

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.32}.png} 
  \\[-5.5em]
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.53}.png} 
\caption{
MC identified by applying 
volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$.
Color shows the projected H$_2$ surface density. {\bf this should be H2 density 1/cm$^{-2}$?!}
% yt.OffAxisProjectionPlot: weight the requested field by the weighting field and integrate along the line of sight.
\label{fig:MC}}
\addtocounter{figure}{-1}
\end{figure*}

@@

In \Fig{h2density}, we show an example of the volumetric H$_2$ density distribution of \flower 
for a given snapshot which includes contributions from its surrounding 7\,kpc.
In \Fig{MC}, we show an example of
the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{
Based on 10$^n$, where $n$ represents the 10 elements that are 
uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of 
$n_{\rm cut}$ adopted and find no significant differences 
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that 
used to plot \Fig{h2density}.
Since the molecular structures identified could 
easily appear as overlapping structures depending on the viewing angle, we 
also plot them in different three-dimensional projections --- so that one can more 
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between 
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr. 
% {\bf TODO: 0.1\,Myr (500 snapshots at $z$\eq9)}

@@

% --------------------
\section{Results}     \label{sec:results}
\subsection{Star Formation History and Cloud Evolution} \label{sec:sfh}

One of the advantages in studying the properties of MCs at 
$z$\ssim6 using simulations is that we can examine how their properties evolve 
as a function of time. 
This is advantageous especially at early cosmic epochs, 
when the densest structures are beginning to form; 
gas is constantly being accreted onto the central galaxy from the cosmic web and 
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting from interactions with these surrounding 
galaxies can disrupt the main disk and arms, likely leading to different dynamical states 
for the molecular structures (e.g., some may disperse while others may agglomerate into more massive 
structures). % mainly expecting differences in alpha_vir, sigma, M_cl.

Given the stochasticity in the \SF history of \flower, 
we show the scaling relations found for two particular snapshots as examples in \Sec{singless},
since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
most extreme variations in the cloud dynamics) --- one of which \flower is 
actively accreting materials from its surrounding (top panel of \Fig{phases}) 
and another of which \flower is undergoing 
a starburst phase after a major merger (bottom panel of \Fig{phases}).

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 23, clip, width=0.45\textwidth]{\figpath/snapshot28_SFR_4Myr.png}  
\caption{
Star formation history of \flower.
% f_gas history? 
\label{fig:SFH}}
\end{figure*}

\begin{figure}[htbp]
\centering
\includegraphics[trim=120 0 0 0, clip, width=0.55\textwidth]{\figpath/star_16.png}  
\\ [-5em]
\includegraphics[trim=120 0  0 0, clip, width=0.55\textwidth]{\figpath/star_27.png}  
\caption{
Projected stellar mass distribution of \flower during the accretion phase
in its early stage of evolution (top) and during a major starburst phase 
after a major merger (bottom).
\label{fig:phases}}
\end{figure}

\subsection{Cloud Scaling Relations} 
Molecular clouds are the natal place for \SF, and thus,
their structure and dynamics hold important clues to understanding 
the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract parameters such as
the virial parameter ($\alpha_{\rm vir}$), 
the ``cloud'' mass ($M_{\rm cl}$), 
the ``cloud'' size ($R$),  
the Mach number ($\mathcal{M}$), 
the velocity dispersion ($\sigma$), and the 
gas surface density ($\Sigma_{\rm gas}$)
to describe/characterize their dynamics.
We show in \Fig{} the MC distributions in terms of their 
molecular gas mass, radius, gas mass fraction ($f_{\rm gas}$\eq$M_{\rm gas}$/($M_{\rm gas}$ + 
$M_*$)). 
% plt.hist($M_{\rm cl}$), color by two different mass range.. ~2E7?
% plt.hist($R_{\rm cl}$), using same color scheme
% for f_gas, same color scheme
We note that the distributions vary for different snapshots, depending on
the gas surface density, the morphology, and the evolutionary stage of \flower.
The highest surface density threshold of $n_{\rm cut}$ yields a ``minimum'' MC mass on
the order of 10$^{6.5}$\,\Msun for the densest MC identified.
Gas mass fractions of the MCs vary between $f_{\rm gas}\approx$xxx$-$0.xx. 
% which may determine the ``cloud'' mass if these MCs are formed due to gravitational 
% instabilities. We show gas fraction as a function of ``cloud'' mass in \Fig{}.
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the 
snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).

We find that the local sound speed ($c_s$) 
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities.
We find comparable velocity dispersion derived by taking the root mean square ($\sigma^{\rm rms}$) versus
that derived using thermal and non-thermal pressure ($\sigma^{P+P_{\rm nt}}$), indicating that 
rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion (i.e., $\sigma$\eq$\sigma^{\rm rms}$).
In \Sec{Q}, we also measure the contributions to the extracted velocity dispersions of the 
MCs due to galactic rotation and shear.

@@

\subsubsection{Single Snapshots: SFR-Mach-$\alpha_{\rm vir}$ Relation}
%M~ 30 in normal spirals \citep{McKee99a}
%M~ 100 in SBs \citep{Downes98a}
In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular 
complexes identified. 
We find a positive correlation between the two quantities, with a Pearson-$R$ coefficient of xxx, 
which is unsurprising given that our simulations include the effect of stellar feedback. That is, 
the high $\mathcal{M}$ can be interpreted as a result of \SF resulting from feedback from 
massive stars.

>>>>

\usepackage{xcolor}
\definecolor{apcolor}{HTML}{b3003b}
\definecolor{dlcolor}{HTML}{FF7F00}
\newcommand{\AP}[1]{({\bf \color{apcolor} AP: #1})}
\newcommand{\DL}[1]{({\bf \color{dlcolor} DL: #1})}

@@

\begin{abstract}
We present results from the first study investigating the dynamical properties of molecular clouds
and their evolution in galaxies at Epoch of Reionization using state-of-the-art cosmological
zoom-in simulation, which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback via
kinetic and thermal energies. We find that ..
\end{abstract}
%\keywords{infrared: galaxies --
%          galaxies: high-redshift --
%          galaxies: ISM --
%          galaxies: evolution --
%          galaxies: starburst --
%          radio lines: ISM}

@@

The growth of galaxies and their subsequent evolution are governed by the baryonic/baryon cycle ---
galaxies accrete gas from the intergalactic medium to fuel \SF (and feed their supermassive blackholes)
and subsequent feedback replenishes and enriches the circumgalactic medium with part of this material.
The general consensus is that the growth of \highz galaxies are triggered/supported by massive
gas inflows from mergers and/or the cosmic web at early cosmic time, when the intergalactic
medium and galaxies themselves are more gas-rich in their star-forming molecular
gas contents compared to present-day galaxies.
% while at a given snapshot, the gas mass fraction maybe low (esp. at high-z when
% the gravitational potential is still increasing), but their gas reservoirs
% are continuously being replenished.
These massive gas inflows in turn trigger gravitational instability, and thus, lead
to the formation of clouds/structures that are typically more massive and denser than those
observed in nearby galaxies, with cloud masses of $M_{\rm cloud}$\eq10$^9$\,\Msun
and sizes on sub-kpc scales (e.g. \citealt{Gabor13a, Hopkins14a, Inoue16a}).
%In cosmological context, minor mergers and external gas accretion can
%significantly impact on disc dynamics and clump formation
%(e.g. Bird et al. 2012, MNRAS, 420, 913; Kyziropoulos et al. 2016, MNRAS, 463, 2210).
Some theoretical works argues that it is in fact the
migration of such giant massive clumps that are responsible for contributing to the
buildup of the bulges of massive galaxies at \z$\sim$0 \citep[e.g.,][]{Ceverino10a}.

At high redshifts, galaxies have higher star formation rates (SFR) and smaller sizes {\bf cite needed?}, thus are expected to have more \ion{H}{2} regions and ionized gas, and more intense radiation stellar feedbacks. Since also the metallicity and dust content should be lower {\bf cite?}, this affects the shielding of UV photons, heating and cooling mechanisms. Such differences in turn can have a role in regulating the thermal and chemical structures of their ISM, and thus, their multi-phase ISM differ from nearby galaxies.
%
Since \highz galaxies are the early stages of evolution of present-day galaxies, studying their ISM properties is essential for understanding how \SF proceed under these more extreme conditions, thereby driving the evolution and assembly history of galaxies since the cosmic dark ages.

The FIR fine-structure lines (e.g., \cii, \nii, and \oiii), and CO/[\ci]~lines are the key diagnostics for
constraining the ISM conditions of galaxies and
provide highly complementary information tracing the different phases of the ISM (ionized,
atomic, molecular; e.g., \citealt{Scoville74a, Rubin85a, Malhotra01a}).
Global measurements of these diagnostics in \highz galaxies
have informed us on their galaxy-wide properties (e.g.,
gas masses, gas temperature, and radiation field intensity).
However, spatially resolving their ISM is needed in order to understand their role in galaxy evolution and
the physics behind their intense \SF (SFR\ssim100$-$3000\,\Msun\,yr\pmOne).
To date, the ISM properties of \highz galaxies
have only been studied observationally in a handful of (strongly-lensed)
galaxies, using spatially resolved tracers such as
dust continuum, and CO and \cii lines (e.g., \citealt{Swinbank11a, Hodge15a, Ferkinhoff15a, Hodge16a},
Leung et al. 2018, submitted).
These studies find that the ISM of $z$\ssim2 galaxies are more
molecular gas-rich, turbulent, and clumpy than nearby galaxies.
\AP{i think the passage to "why we focus on eor galaxies" should be detailed a bit more}
However, it is still unclear how \SF proceed in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6
that dominates  \SF at the epoch of reionization which is responsible for producing the
ionizing photons that reionized the universe.

@@

This paper is structured as follows.
\AP{TBM}
In \Sec{sim}, we describe the setup of our simulation and the properties of our galaxy (\flower),
and describe the method used to identify its molecular gas complexes (MC).
In \Sec{results}, we present scaling relations based on
the MC identified and compare them with observations of molecular
(sub-)structures seen in nearby and \z$>$\,0 galaxies.
We present Toomre stability analysis in \Sec{Q} and
the cumulative mass distribution of the MCs in \flower in \Sec{cmf}.
In \Sec{diss}, we discuss the results and implications of our findings,
and present our conclusions in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481,
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678,
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

@@

\ncode{Serra} is a cosmological zoom-in simulation performed using Eulerian hydrodynamics and
adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high baryonic density).
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier2002a} as the AMR backend.
%\ncode{Serra} uses sub-grid models that simultaneously account for the radiative transfer, clumpy structure, and photoevaporation feedback in the neutral diffuse and molecular gas.
Our simulation covers a co-moving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of 30\,pc (at \z$\sim$\,6) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun in the finest level. Such a physical scale is close to the size scale of molecular cloud complexes and giant molecular clouds (GMCs), as seen in nearby galaxies \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.
% (Giant molecular clouds: L>22pc, m>10^5 Msun) in MW.
We include chemical network in the simulation to trace $\rm{H}$, $\rm{H}^{+}$, $\rm{H}^{-}$, $\rm{He}$, $\rm{He}^{+}$, $\rm{He}^{++}$, $\rm{H}_2$, $\rm{H}_2^{+}$ \citep{Grassi14a,Bovino16a}.
Of particular importance to our study here is that our simulation includes non-equilibrium formation of molecular hydrogen (done on-the-fly) to determine the H$_2$ abundance (see \citealt{Pallottini17b} for effects of chemistry affected by non-equilibrium versus equilibrium H$_2$ formation).

% radiative feedback --> NT pressure
Star formation is modeled using a H$_2$-based prescription of the Schmidt-Kennicutt relation \citep{Krumholz09a}. We adopt stellar tracks from \ncode{starburst99} and include stellar feedback from supernova, OB/AGB stars to account for energy dissipations. To couple the feedback to the gas, we employ sub-grid modeling for blastwaves, e.g., to account for the potential lost of energy inside the cell when supernovae explode. The energy dissipated is then injected into the ISM in the form of kinetic and thermal energy, and radiation pressure (on the dust and gas) is also included \citep[see][for details]{Pallottini17a}.

Details on the properties of \flower, the main galaxy in our simulation, are discussed in \citet{Pallottini17b}.
%
Briefly, by \z$\sim$6, \flower is a LBG hosted in a dark matter halo of mass $M_{\rm DM}\simeq$\,10$^{10}$\,\Msun at the center of a cosmic web knot, and accretes mass from the intergalactic medium mainly via three filaments of length $\simeq$\,100\,kpc. At \z$\sim$6, \flower has a stellar mass of $M_*\simeq$\,3\E{10}\,\Msun, metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a globally-integrated SFR of $\simeq$\,100\,\Msun\,yr\pmOne. It is therefore a prototypical galaxy at \z$\sim$6.

\subsection{Star Formation History} \label{sec:sfh}

\AP{i moved the section here, as I see it as part of motivation for the workflow; however, at the moment I do not see the stellar mass maps as figure that are needed; if they stay i would label their evolutionary stage in the SFR history plot.}

One of the advantage of studying the dynamical properties of molecular structures at
$z$\ssim6 in simulation is the fact that we can examine how their properties evolve
as a function of time.
This is advantageous especially at early cosmic epochs,
when the densest structures are beginning to form;
gas is constantly being accreted onto the central galaxy from the cosmic web and
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting from interactions with these surrounding
galaxies can disrupt the main disk and arms, likely leading to different dynamical states
for the molecular structures (e.g., some may disperse while others may agglomerate into more massive
structures). % mainly expecting differences in alpha_vir, sigma, M_cl.

Given the stochasticity in the \SF history of \flower,
we show the scaling relations found for two particular snapshots \AP{in the text I would refer to snapshots as to evolutionary stages of the galaxy (and make the link between the two in the method section)} as examples in \Sec{singless},
since they represent the extreme evolutionary stages of \flower (and thus, likely bracket the
most extreme variations in the cloud dynamics) --- one of which \flower is
actively accreting materials from its surrounding (top panel of \Fig{phases})
and another of which \flower is undergoing
a starburst phase after a major merger (bottom panel of \Fig{phases}).

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 23, clip, width=0.45\textwidth]{\figpath/snapshot28_SFR_4Myr.png}
\caption{
	Star formation history of \flower \AP{if possible I would combine it with Fig. \ref{fig:phases} (as in the talk), or remove
	Fig. \ref{fig:phases}, as at the moment it does not add much to the discussion.
	}.
% f_gas history?
\label{fig:SFH}}
\end{figure*}

\begin{figure}[htbp]
\centering
\includegraphics[trim=120 0 0 0, clip, width=0.55\textwidth]{\figpath/star_16.png}
\\ [-5em]
\includegraphics[trim=120 0  0 0, clip, width=0.55\textwidth]{\figpath/star_27.png}
\caption{
Projected stellar mass distribution of \flower during one of its accretion phases
at an early stage of its evolution (top) and during one of its major starburst phases
after a major merger (bottom).
\label{fig:phases}}
\end{figure}

\subsection{Structure identification} \label{sec:method}

To identify the molecular complexes, we use a customized version of the clump finder algorithm available in the \ncode{python} package \ncode{yt} \citep{Turk2011a}, which was initially described in \citet{Smith09a} but this function has been modified since then.
%
The latest version of the default \ncode{yt} clump finder decomposes the cells in the simulation into non-overlapping tiles, which are stored in a k-dimentional tree (aka k-d tree). It then identifies the contours of a variable field (e.g., density field) within a tile and connects them across the tiles. In the customized version used for this study, \AP{the following is true but I do not think we should write it in this way ...} \DL{right, will change when we submit paper, just being sarcastic here.} we modified \ncode{yt} in order for it to actually work.

In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).

\AP{maybe we can refer to the PPP vs PPV method discussion in Mordecai's paper}
We note that this process is in essence similar to
identifying molecular structures based on the noise levels of surface density maps
observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
as commonly adopted in observational studies (e.g., identifying
``clumps'' based on/after applying $\sigma$-clipping,
using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind},
and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a}).

\begin{figure}[htbp]
\centering
\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}
\caption{
Volumetric H$_2$ density distribution of \flower taken from a single snapshot.
\label{fig:h2density}}
\end{figure}

\begin{figure*}[htbp]
 \centering
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.32}.png}
  \\[-5.5em]
  \includegraphics[scale=0.7]{\figpath/{dual_16_ncut_0.53}.png}
\caption{
MC identified by applying
volumetric H$_2$ density cuts of
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$.
	Color shows the projected H$_2$ surface density. {\bf this should be H2 density 1/cm$^{-2}$?!} \AP{if i recall correctly, this is not the projected h2 density, but the mass averaged h2 density field. in any case, we should compress the information, by having a less figures showing multplie cuts (e.g. 3 of them by using thinner lines should suffice in conveining the overview properly); additionally, we should convince yt to plot a proper label for the colorbar, and remove the trailing right axes labels (that are still there despite our efforts)}
% yt.OffAxisProjectionPlot: weight the requested field by the weighting field and integrate along the line of sight.
\label{fig:MC}}
\addtocounter{figure}{-1}
\end{figure*}

@@

In \Fig{h2density}, we show an example of the volumetric H$_2$ density distribution of \flower
for a given snapshot which includes contributions from its surrounding 7\,kpc.
We note that the distribution is almost flat for $n_{\rm H2}\gtrsim1\,\cc$ and it samples the range where ``clumps/structures'' are 
found based on the Minkovsky analysis presented by \citet{Pallottini17b}.
In \Fig{MC}, we show an example of the molecular structures identified by applying volumetric H$_2$ density cuts of \AP{I would directly use labels in logspace} $n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{Based on 10$^n$, where $n$ represents the 10 elements that are uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of
$n_{\rm cut}$ adopted and find no significant differences
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that
used to plot \Fig{h2density}.
Since the molecular structures identified could
easily appear as overlapping structures depending on the viewing angle, we
also plot them in different three-dimensional projections --- so that one can more
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr.

@@

\section{Results}     \label{sec:results}

\subsection{Cloud Scaling Relations}
\AP{I see 2 main possible approaches to the presentation of the results
%
(a) focus on a single snapshot, analyze the cloud scaling relation by varing the cuts and then by varing the snapshot; after that one can discuss the stability (toomre analysis) of the clumps (that should help in discussing the origin) and the CMF (more speculative, because of the resolution issues).
%
(b) discuss each scaling relation one at a time; probabily in this case an introductionary subsection is needed to explain that different cuts yields no qualitative differences; toomre and CMF as before.
%
Note that -- in both cases -- alternatively toomre analysis can be done at the beginning of the result section(s).
%
I think that (b) might be a little bit more appealing, since all the plot with similar quantities (e.g. the larson relation for multiple cuts and snapshots) are in the same place (or, even better, page).
%
Of course alternative approaches are possible, but right now these two seem to be the more natural ones.
}

Molecular clouds are the natal place for \SF, and thus,
their structure and dynamics hold important clues to understanding
the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract parameters such as
the virial parameter ($\alpha_{\rm vir}$),
the ``cloud'' mass ($M_{\rm cl}$),
the ``cloud'' size ($R$),
the Mach number ($\mathcal{M}$),
the velocity dispersion ($\sigma$), and the
gas surface density ($\Sigma_{\rm gas}$)
to describe/characterize their dynamics.
We show in \Fig{} the MC distributions in terms of their
molecular gas mass, radius, gas mass fraction ($f_{\rm gas}$\eq$M_{\rm gas}$/($M_{\rm gas}$ +
$M_*$)).
% plt.hist($M_{\rm cl}$), color by two different mass range.. ~2E7?
% plt.hist($R_{\rm cl}$), using same color scheme
% for f_gas, same color scheme
We note that the distributions vary for different snapshots, depending on
the gas surface density, the morphology, and the evolutionary stage of \flower.
The highest surface density threshold of $n_{\rm cut}$ yields a ``minimum'' MC mass on
the order of 10$^{6.5}$\,\Msun for the densest MC identified.
Gas mass fractions of the MCs vary between $f_{\rm gas}\approx$xxx$-$0.xx.
% which may determine the ``cloud'' mass if these MCs are formed due to gravitational
% instabilities. We show gas fraction as a function of ``cloud'' mass in \Fig{}.
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the
snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).

We find that the local sound speed ($c_s$)
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities.
\AP{i would put the following as a footnote or this point might be moved; alternatively these points (see also the emails) can be treated when dealing with the stability analysis}
We find comparable velocity dispersion derived by taking the root mean square ($\sigma^{\rm rms}$) versus
that derived using thermal and non-thermal pressure \AP{i would not introduce additional symbols if they are not used elsewhere} ($\sigma^{P+P_{\rm nt}}$), indicating that
rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion (i.e., $\sigma$\eq$\sigma^{\rm rms}$).
In \Sec{Q}, we also measure the contributions to the extracted velocity dispersions of the
MCs due to galactic rotation and shear.

@@

\subsubsection{Single Snapshots: SFR-Mach-$\alpha_{\rm vir}$ Relation}
%M~ 30 in normal spirals \citep{McKee99a}
%M~ 100 in SBs \citep{Downes98a}
\AP{here (or before) we should explain how the sfr is calculated (i.e. integrating over the recent sfr history of star within the clump)}
In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular
complexes identified.
We find a positive correlation between the two quantities, with a Pearson-$R$ coefficient of xxx,
which is unsurprising given that our simulations include the effect of stellar feedback. That is,
the high $\mathcal{M}$ can be interpreted as a result of \SF resulting from feedback from
massive stars.

\subsubsection{Schmidt-Kennicutt Relation}
\AP{I would maybe move this stuff into the appendix}
As benchmarking, we check the SK relation using the SFR and gas surface densities of the clouds. {\bf remind Pallo to look into this}.
